Magnetized Polish doughnuts revisited

### 2017-01-19 paper.tex
a bit of work

%--------------------------------------------------------------------
\section{Results}

\begin{figure*}
\centering
\includegraphics[scale=0.4]{images/1.pdf}
\includegraphics[scale=0.4]{images/2.pdf}
\caption{test density plots}
           \label{FigGam}%
 \end{figure*}

>>>>

%%%%%%%%%
\section{Results}
%%%%%%%%%

Figure~\ref{komissarov} corresponds to the same constant specific angular momentum model presented by~\citet{Komissarov:2006}. The comparison shows that our approach can reproduce those previous results with good agreement. {\bf Complete description.}

\begin{figure*}
\centering
\includegraphics[scale=0.32]{images/1_A.pdf}
\hspace{-1.2cm}
\includegraphics[scale=0.32]{images/1_B.pdf}
\hspace{-0.8cm}
\includegraphics[scale=0.32]{images/1_C.pdf}
\caption{Comparison with Komissarov's solution for a constant angular momentum model.}
           \label{komissarov}%
 \end{figure*}

%\begin{figure*}
%\centering
%\includegraphics[scale=0.4]{images/1.pdf}
%\includegraphics[scale=0.4]{images/2.pdf}
%\caption{test density plots}
%           \label{FigGam}%
% \end{figure*}
